---
title: "Replicating Sustainable youth employment quality management: The impact of robotization in China by Fucheng Liang and Yi Liu"
format: pdf
author: Jesse Brandt, Alyssa Langmeyer, Veena Seshadri
date: June 10, 2025
---
Load packages
```{r}
#| output: false
library(tidyverse)
library(readxl)
library(readr)
library(ExPanDaR)
library(lme4)
library(miceadds)
```

## Load the data (cleaned and truncated)

```{r}
robots <- read_csv("../Data/robots_cleaned.csv")
```

# Table 2: Summary Statistics.

```{r}
#select relevant columns
selected_variables <- robots %>%
  select(Quality, Robot, age, gender, marriage, health, lnGDP, structure, lnaverwage)
#get summary statistics
mapply(FUN = \(x) c(N = length(x), mean = mean(x), sd = sd(x), min = min(x), max = max(x)),
       selected_variables) %>%
  t()
```


```{r}
#| include: false
robots %>%
  summary()
```



# Table 3: Linear model.
Our results do not yet match theirs. Individual FE is unclear.


## Mixed effects model (column 1)
```{r}
me_model <- lmer(data = robots, formula = Quality ~ Robot + age + gender + marriage + health + lnGDP
     + structure + lnaverwage + as.factor(year)+ as.factor(province) + (1|id))
summary(me_model)
```


## Fixed effects model (column 2)
```{r}
fe_model <- lm.cluster(data = robots, formula = Quality ~ Robot + age + gender + marriage + health + lnGDP
                     + structure + lnaverwage + as.factor(year) + as.factor(province),
                     cluster = "id")
summary(fe_model)

```


```{r}
#| eval: false
model1 <- lm(data = robots, formula = Quality ~ Robot + age + gender + marriage + health + lnGDP
   + structure + lnaverwage + as.factor(year) + as.factor(province))
model2 <- lm(data = robots, formula = Quality ~ Robot + age + gender + marriage + health + lnGDP + structure + lnaverwage)

model.1.summary <- summary(model1)
model.2.summary <- summary(model2)

#model including year FE and region FE
model.1.summary
#model 1 with province and year FE not shown
model.1.summary$coefficients[1:9,1:4]
#model without year FE and region FE
model.2.summary

#model including id - filtered to include only ids with more than one observation
duplicate_ids <- robots %>%
  group_by(id) %>%
  mutate(count = length(id)) %>%
  filter(count>1)

fe_model3 <- lm(data = duplicate_ids, formula = Quality ~ Robot + age + gender + marriage + health + lnGDP
                + structure + lnaverwage + as.factor(year) + as.factor(province) + as.factor(id))

#Next model takes a long time to run. Is it equivalent to fe_model3?
start_time <- Sys.time()
# fe_model4 <- lm(data = robots, formula = Quality ~ Robot + age + gender + marriage + health + lnGDP
#                 + structure + lnaverwage + as.factor(year) + as.factor(province) + as.factor(id))
end_time <- Sys.time()

elapsed_time <- end_time-start_time

cat("Time to run model:", elapsed_time)
model.3.summary <- summary(fe_model3)
model.3.summary$coefficients[1:9,1:4]
```


## Random effects model (column 3)
Note: in the paper, column 3 is the same as column 1, but the text indicates that it should be the random effects model.
```{r}
re_model <- lmer(data = robots, formula = Quality ~ Robot + age + gender + marriage + health + lnGDP + structure + lnaverwage + (1|year) + (1|province) + (1|id))
summary(re_model)
```



```{r}

```

# Table 4: Results of endogeneity test and robustness test.


# Table 5: Heterogeneity analysis results.
```{r}
#| output: false
#Gender
man <- filter(robots, gender == 1)
woman <- filter(robots, gender ==0)

#Education
unique(robots$education)
count(robots, education)
690 + 4763 # 0 and 1 are primary
# 2 is middle
# 3 is university
primary <- filter(robots, education == 0 | education ==1)
middle <- filter(robots, education == 2)
university <- filter(robots, education ==3)

#Age groups
age_1 <- filter(robots, age >= 17 & age <= 25)
age_2 <- filter(robots, age >= 26 & age <= 35)

# Regional employment
large <- filter(robots, reg_labor > mean(reg_labor))
small <- filter(robots, reg_labor <= mean(reg_labor))

#temp


fit_fe_model <- function(dataset){
  model <- lm.cluster(data = dataset, formula = Quality ~ Robot + age + gender + marriage + health + lnGDP
             + structure + lnaverwage + as.factor(year) + as.factor(province),
             cluster = "id")
  model_summary <- summary(model)
  return(model_summary[2,1:4])
}

fit_fe_model(large)
tbl <- map(.x = list(man,woman,primary,middle,university,large,small), .f = fit_fe_model) %>%
  data.frame()
names(tbl) <- c("Man", "Woman", "Primary", "Middle", "University", "Large", "Small")

rownames(tbl)[1] <- "Estimate (Robot)"


```
```{r}
tbl
```

# Table 6: Results of mechanism analysis.

# Table 7: Results of regulatory effect analysis.

# Table 8: Results of he effectiveness nalysis of employment promotion measures. 