---
title: "Replicating Sustainable youth employment quality management: The impact of robotization in China by Fucheng Liang and Yi Liu"
format: pdf
author: Jesse Brandt, Alyssa Langmeyer, Veena Seshadri
date: June 10, 2025
---
Load packages
```{r}
#| output: false
library(tidyverse)
library(readxl)
library(readr)
library(ExPanDaR)
```

## Load the data & Truncation
```{r}
robots <- read_excel("datas002.xlsx")
trunc.robots <- treat_outliers(robots)
```

# Table 2: Summary Statistics.
```{r}
#select relevant columns
selected_variables <- robots %>%
  select(Quality, Robot, age, gender, marriage, health, lnGDP, structure, lnaverwage)
#get summary statistics
mapply(FUN = \(x) c(N = length(x), mean = mean(x), sd = sd(x), min = min(x), max = max(x)), 
       selected_variables) %>%
  t()

```
```{r}
#select relevant columns
selected_variables <- trunc.robots %>%
  select(Quality, Robot, age, gender, marriage, health, lnGDP, structure, lnaverwage)
#get summary statistics
mapply(FUN = \(x) c(N = length(x), mean = mean(x), sd = sd(x), min = min(x), max = max(x)), 
       selected_variables) %>%
  t()
```


```{r}
#| include: false
robots %>%
  summary()
```
Next steps might involve trying to construct the Quality variable according to the methods described in the paper.

## Creating Quality variable again
Quality is defined in Table 2 as "Wages paid on an hourly basis," so we divide wage by workhours to get Quality.

```{r}
robots <- robots %>%
  mutate(Quality2 = wage/workhours)
mean(robots$Quality2)
sd(robots$Quality2)
min(robots$Quality2)
max(robots$Quality2)
```

# Table 3: Linear model.
These are my two attempts to recreate the linear models in Table 3. In both, the association between Robot and Quality is not significant.
```{r}
lm(data = trunc.robots, formula = Quality ~ Robot + age + gender + marriage + health + lnGDP
   + structure + lnaverwage + as.factor(year) + as.factor(province)) %>%
  summary()
lm(data = trunc.robots, formula = Quality ~ Robot + age + gender + marriage + health + lnGDP
   + structure + lnaverwage) %>%
  summary()
```



# Table 4: Results of endogeneity test and robustness test.


# Table 5: Heterogeneity analysis results.

# Table 6: Results of mechanism analysis.

# Table 7: Results of regulatory effect analysis.

# Table 8: Results of he effectiveness nalysis of employment promotion measures. 